---
title: "Bladder Cancer Analysis"
author: "Zachary McCaw"
date: "2020-12-21"
output: 
  html_document:
    theme: spacelab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  results = "hold", 
  fig.align = "center"
  )
```

## Data

The analysis includes all data in `survival::bladder1` treated with `placebo` or `thiotepa`, and excluding 1 subject (`id == 1`) whose observation `start` and `stop` times were both equal to zero. 

## LWYY Analysis

#### Without Covariate Adjustment

```{r}
load(file = "lwyy.RData")
library(survival)
summary(lwyy0)
```

#### With Covariate Adjustment

```{r}
summary(lwyy1)
```

## AU MCF Analysis

### Composite Endpoint of Recurrence or Death

```{r}
data <- readRDS(file = "../Data/bladder_data.rds")
cmp_data <- data
cmp_data$status[cmp_data$status == 2] <- 1
source("../Rscripts/PlotMCF.R")

PlotMCFs(data = data, title = "Composite Endpoint", y_lim = c(0, 3), x_max = 60)
```

#### Baseline Analysis

```{r}
load("../Results/aumcf.RData")
fit_comp_base
```

#### Augmentation Analysis

```{r}
fit_comp_aug
```

### Recurrence with Death as a Competing Risk

```{r}
data <- readRDS(file = "../Data/bladder_data.rds")
PlotMCFs(data = data, title = "Competing Risk", y_lim = c(0, 3), x_max = 60)
```

#### Baseline Analysis

```{r}
fit_cr_base
```

#### Augmentation Analysis

```{r}
fit_cr_aug
```


